---
title: "Educational facilities"
author: "Ama Darko"
date: "1/7/2022"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Following Gecomputation with R by Robin Lovelace Chapter 2.

#### Load packages and data

```{r packages, include=FALSE}
pacman::p_load(tidyverse,tidylog, shiny, flextable,tmap,sf, magrittr)
#,geocompkg, spData, spDataLarge, terra,

```

```{r load_data, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
edu_facilities<-read_sf("data/hotosm_gha_edu_facilities_points_shp/hotosm_gha_education_facilities_points.shp")
```

```{r geolayers, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#check what layers are loaded
gdalUtils::ogrinfo("data/hotosm_gha_education_facilities_gpkg/hotosm_gha_education_facilities.gpkg") |> 
  cat(sep="\n")
```

#### Data Cleaning

Checking what columns/ features are present in the data set.

```{r include=FALSE}
source("code/Ghana_admin2_map.R")
names(edu_facilities)
```

The name column is the name of the school and the "amenity" column shows what type of school it is.

*Identifying if there are NA values in the name and amenity columns*

```{r check_na}
#check names that are NA
summary(is.na(edu_facilities$name))

#check amenity that are NA
summary(is.na(edu_facilities$amenity))


```

*Changing the value of amenity from School to Primary for (basic, preparatory, primary schools)*

```{r amenity, eval=FALSE, include=FALSE}
#change to title case
edu_facilities$amenity<-str_to_title(edu_facilities$amenity)

edu_facilities$amenity<-if_else((str_detect(edu_facilities$name,
                                       "Basic|Preparatory|Primary")),"Primary",edu_facilities$amenity)

         
#summary(edu_facilities$amenity)


```

The initial data set contained the geolocations of 5,502 educational facilities in Ghana.
Using the code block below, 2376 rows were removed that had NA in both name and amenity columns.
Thus, the resulting data set set has 3126 rows.

Also, amenity was converted from character column to a factor column

```{r load_data_processing_code, eval=FALSE, include=FALSE}
source("code/Ghana_admin2_map.R")
```

```{r create_df_without_NA_in_name_or_amentity, eval=FALSE, include=FALSE}


#edu_n1<-na_name(try)
#edu_n2<-na_name(polygon)
#checking about duplicates


#drop unused levels
edu_new<-na_name(edu_facilities)
edu_new%<>%
   mutate(across(c(amenity),droplevels))


#summary(is.na(edu_new$name))

#summary(is.na(edu_new$amenity))

```

*Check current categories of amenity column*

```{r categories_amenity}
summary(edu_new$amenity)


#changing name of amenity level "school" to Primary 1-Secondary 12

#levels(edu_name_not_null$amenity)<- c("College","")
```

*Load Ghana administrative boundaries*

```{r load_school_attendance_data, echo=TRUE}
source("code/School attendance data.R")
```

This R Markdown document is made interactive using Shiny.
Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately.

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

\`

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function.
This example embeds a [Shiny application](https://aowusuda.shinyapps.io/Step_up_education_in_Ghana/) located in another directory:

```{r shiny_app, echo=FALSE}

knitr::include_app("https://aowusuda.shinyapps.io/Step_up_education_in_Ghana/")

```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used.
This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.
