---
title: "mics_ch5_17"
author: "ktemadarko"
date: "2022-01-19"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse,magrittr,here)
```

About the data set.

This data set has 8965 observations of 285 variables from the Ghana 2017/18 Multiple Indicator Cluster Survey.
The data is available to the public with registration at the [<https://mics.unicef.org/surveys>](https://mics.unicef.org/surveys) website.

Each observation represents the responses a mother gave to a questionnaire about her child aged between 5 and 17 in Ghana.
We focused on the questions about foundational skills of Ghanaian children 5-17 years.
These questions can be found on pages 574 591 to 619.
[View Ghana 2017/18 MICS Questionnaire here](https://mics-surveys-prod.s3.amazonaws.com/MICS6/West%20and%20Central%20Africa/Ghana/2017-2018/Survey%20findings/Ghana%202017-18%20MICS%20Survey%20Findings%20Report_English.pdf).

The data is loaded and stored in the variable ch5_17

```{r load_data message=FALSE, warning=FALSE}
ch5_17 <- read_sav(here::here("data/fs.sav"))
```

The data was filtered and rows where consent for the interview was not given or the interview was not completed or the interview

```{r}
ch5_17_mini<- ch5_17%>%
  #filtering data FS10==1 for consent given and FS17 for interview completed.
  #FS13==11 means interview in English & FS14==11 means English is the native language of the responder
                    filter(FS10==1 & FS17==1 & FS13==11 & FS14==11)%>%
                    select(c(1:6,8),
                           starts_with("CB"), #child's background
                           starts_with("PR"), #parental involvement
                           starts_with("FL")) #foundational skills


ch5_17_small<- ch5_17%>%
  #filtering data FS10==1 for consent given and FS17 for interview completed.
  #FS13==11 means interview in English & FS14==11 means English is the native language of the responder
                    filter(FS10==1 & FS17==1 & FS13==11)%>%
                    select(c(1:6,8),
                           starts_with("CB"), #child's background
                           starts_with("PR"), #parental involvement
                           starts_with("FL")) #foundational skills
```
